\documentclass[a4paper, oneside, final]{scrartcl} % Paper options using the scrartcl class

\usepackage{scrlayer-scrpage} % Provides headers and footers configuration
\usepackage{titlesec} % Allows creating custom \section's
\usepackage{marvosym} % Allows the use of symbols
\usepackage{tabularx,colortbl} % Advanced table configurations
\usepackage{ebgaramond} % Use the EB Garamond font
\usepackage{microtype} % To enable letterspacing
\usepackage[none]{hyphenat}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule] % Section formatting

\addtolength{\voffset}{-0.5in} % Adjust the vertical offset - less whitespace at the top of the page
\addtolength{\textheight}{3cm} % Adjust the text height - less whitespace at the bottom of the page

\newcommand{\gray}{\rowcolor[gray]{.90}} % Custom highlighting for the work experience and education sections
\newcommand{\lightgray}{\rowcolor[gray]{.95}} % Intro

%----------------------------------------------------------------------------------------

\begin{document}

\begin{center} % Center everything in the document

%----------------------------------------------------------------------------------------
%	HEADER SECTION
%----------------------------------------------------------------------------------------

{\fontsize{20}{36}\selectfont\scshape\textls[200]{Jordan David Richmond}} % Your name at the top

\vspace{1.5cm} % Extra whitespace after the large name at the top

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience / Volunteering}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
	\gray Period & \textbf{September 2022 --- Present}\\
	\gray Employer & \textbf{Outwood Academy Kirkby}\\
	\gray Job Title & \textbf{Science Technician}\\
	& Head of the prep room, producing practicals, demos and experiments for teachers and students.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
	\gray Period & \textbf{July 2022 --- August 2022}\\
	\gray Employer & \textbf{Future Products Ltd}\\
	\gray Job Title & \textbf{Factory Operative}\\
	& Operating a circular saw to cut plastics and aluminium components, a welding machine to weld cills for windows and a wrapping machine to wrap up components for transport.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{July 2016 --- January 2019}\\
\gray Employer & \textbf{Lidder Care Ltd}\\
\gray Job Title & \textbf{Maintenance Assistant}\\
       & Assistant in the maintenance department carrying out repairs, decorating, technology advisor and health and safety checks: fire equipment and wheelchairs.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{November 2019 --- Present}\\
\gray Employer & \textbf{Keele University Observatory}\\
\gray Job Title & \textbf{Observatory Astronomer (Volunteering)}\\
       & Staff Volunteer at Keele Observatory every Tuesday.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
	\gray Period & \textbf{October 2017 --- July 2018}\\
	\gray Employer & \textbf{The Samworth Church Academy}\\
	\gray Job Title & \textbf{Laboratory Assistant (Volunteering)}\\
	& Assisting the senior lab technician in duties such as preparing experiments for classes, tidying up and storage and helping with science club activities. (All jobs and tasks were carried out with authorisation from the senior laboratory technician and senior leadership member).
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{3cm}X}
\gray Period & \textbf{September 2019 --- October 2022}\\
\gray Qualification & \textbf{Bachelor of Science in Astrophysics with Education}\\
\gray Grade & \textbf{Third Class Honours}\\
\gray Institution & \textbf{Keele University}\\
%& Extra information about degree
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{3cm}X}
\gray Period & \textbf{September 2018 --- June 2019}\\
\gray Qualification & \textbf{Foundation Degree in Science}\\
\gray Grade & \textbf{Second Class Honours (Division I) with progression onto undergraduate degree}\\
\gray Institution & \textbf{Keele University Foundation Centre}\\
%& Extra information about degree
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{3cm}X}
	\gray Period & \textbf{September 2016 --- July 2018}\\
	\gray Qualification & \textbf{Level 3 National Extended Diploma in Applied Science}\\
	\gray Grade & \textbf{D*DD}\\
	\gray Institution & \textbf{The Samworth Church Academy}\\
	%& Extra information about degree
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{3cm}X}
	\gray Period & \textbf{September 2013 --- July 2016}\\
	\gray Qualification & \textbf{GCSE}\\
	\gray Grade & \textbf{9 GCSE's Grade B-D}\\
	\gray Institution & \textbf{The Samworth Church Academy}\\
	%& Extra information about degree
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\section{Key Skills}

Communication

\begin{itemize}
	\item Developed skills in interpersonal communication and public speaking with colleagues and members of the public whilst working as an observatory staff and astronomer. Gained leadership and mentoring skills through volunteering at Keele observatory.
\end{itemize}

Organisation

\begin{itemize}
	\item Balanced a challenging mix of university studies and volunteer work.
	\item Assisted in planning and delivering events. Mainly as part of the 2020 astronomical event 'The Great Conjunction' in partnership with Keele University. As well as this, I have contributed to assisting and planing private observatory events.
\end{itemize}

IT \& Tech Skills

\begin{itemize}
	\item Proficient in Python for use in data analysis.
	\item 12 weeks experience using Scientific Linux for the purposes of research project.
	\item \LaTeX \space software is my go to document editor due to its ease and multifunctionality in creating posters, presentations, problem sheets and exams / tests.
\end{itemize}

Other Skills

\begin{itemize}
	\item Active Listening - This has been an asset during my degree programme and at the observatory.
	\item Problem Solving - I have faced many problem solving tasks as part of my degree programme.
	\item Time Management - I make sure to plan my time efficiently so I meet my deadlines.
\end{itemize}

%----------------------------------------------------------------------------------------
%	NOTEWORTHLY WORK
%----------------------------------------------------------------------------------------

\section{Noteworthy Work}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
	\gray Year & \textbf{2018}\\
	\gray Format & \textbf{Investigative project}\\
	\gray Grade & \textbf{Distinction}\\
	\gray Title & \textbf{\textit{An investigation to look at the different oxidation states and the complex ions of the period 4 transition metals and ways to chemically analyse them}}\\
	& This unit enables learners to gain an understanding and the skills required to undertake an investigative project. Choose one topic area that interests you and this will form the basis of your investigative project. You will carry out a scientific literature search and review, considering the project’s aims and objectives, then produce a realistic plan and carry out the project safely using your scientific investigation skills, project management skills and what you have learnt from the other units. Finally, you will prepare an evaluative report that will consider the project outcomes and suggest amendments that may have improved those outcomes.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
	\gray Year & \textbf{2021}\\
	\gray Format & \textbf{Research Note}\\
	\gray Grade & \textbf{Second Class Honours (Division I)}\\
	\gray Title & \textbf{\textit{Investigations into the Local Stellar Population of the Large Magellanic Cloud, Red Giant IRAS04496-6958 and Open Cluster HS66-33}}\\
	& Using Scientific Linux to perform astrophysical techniques such as PSF (Point Spread Function) Photometry to calculate distance to the LMC and the age of stars within.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
	\gray Year & \textbf{2022}\\
	\gray Format & \textbf{Dissertation}\\
	\gray Grade & \textbf{Second Class Honours (Division II)}\\
	\gray Title & \textbf{\textit{Insight into the History and Characteristics of the Chemically Peculiar Stars}}\\
	& Investigating the four main chemically peculiar stars from history to spectra.
\end{tabularx}

\vspace{12pt}

%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\section{Awards}

\begin{itemize}
	\item Participant in KeeleSU Volunteer Project: Bronze (25 hrs), Silver (50 hrs) and Gold (100 hrs).
	\item JJG Training Courses: Challenging Behaviour, Mental Capacity and Deprivation of Liberties and Fire Safety, Awareness, Evacuation and Use of Extinguishers.
	\item Academic Poster on the topic of 'Water Sources on the Lunar Surface'.
\end{itemize}


\end{center}

\end{document}